### 2023-11-03 ms.qmd
Update ms.qmd

# Bayesian model delicata
  deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)

>>>>

# Bayesian model delicata
  deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)
  plot(deli_mod)
